
\begin{thebibliography}{100}

\bibitem{}{Alblas, J.(2012), ``Hedonic Pricing of Green Spaces: The influence of proximity and view'', Speciale, Københavns Universitet.}

\bibitem{}{Alonso, W.(1964), ``Location and Land Use - Towards a General Theory of Land Rent'', \textit{Harvard University Press}.}

\bibitem{}{Anselin, L.(2010), ``Thirty years of spatial econometrics'', \textit{Papers in Regional Science}, 89: 3–25.}

\bibitem{}{Bae,  C.C, Jun, M. og Park, H. (2003), ``The impact of Seouls's Subway line 5 on residential property values'', \textit{Transport policy}, 10 pp. 85-94.}

\bibitem{}{Bowes, D. og Ihlanfeldt, K.R.(2001), ``Identifying the impact of rail transit Stations on Residential Property Values'',  \textit{Journal of Urban Economics}, vol. 50 pp. 1-25.}

\bibitem{}{Buja, A., Hastie, T. og Tibshirani, R. (1989), ``Linear Smoothers and Additive Models'', \textit{The Annuals of statistics}, Vol. 17, No.2, pp. 453-555.}

\bibitem{}{Chen, h., Anthony, R. og Dueker, K. J. (1997), ``Measuring the Impact of Light Rail Systems on singel Family Home Values: A Hedonic Approach with GIS Application'', \textit{Center for Urban Studies College of Urban and Public Affairs Portland State University}, Discussion Paper 97-3. 
} 

\bibitem{}{Chen, j. og Hao, Q.(2008), ``The impact of distance to CBD on housing prices in shanghai: a hedoniv analysis'', \textit{Journal of Chinese Economic and Business Studies}, Vol. 6, No. 3 pp. 291-302.}

\bibitem{}{Chrisander, R. (2011), ``En samfundsøkonomiske analyse af metrocity ringen'', Bachelorprojekt, DTU.}

\bibitem{}{Day, B.(2001), ``The Theory of Hedonic Markets: Obtaining welfare measures for changes in
environmental quality using hedonic market data'' , Economics for the Environment Consultancy.}

\bibitem{}{Dewees, D.N.(1976), ``The effect of ta Subway on residential Property Values in Toronto'', \textit{Journal of Urban Economics}, vol. 3 pp. 357-369.}

\bibitem{}{Erhvervs- og Byggestyrelsen (2007), ``Overblik over fejl og mangler i BBR''.}

\bibitem{}{Freeman, A. M. (1979), ``Hedonic Prices, Property Values and Measuring enviromental Benefits: A survey of the Issues'', \textit{The Scandinavian journal of economics}, Vol. 81, No. 2, pp. 154-173.}

\bibitem{}{Hand, D., Mannila, H. og Smyth, P. (2001), ``Principles of Data Mining'', \textit{A Bradford Book, The MIT Press}.}

\bibitem{}{Hastie, T. og Tibshirani, R. (1986), ``Generalized Additive Models'', \textit{Statistical Science}, Vol. 1, No. 3, pp. 297-318.}

\bibitem{}{Kolstrup, K.(2006), ``A Hedonic Price Study of the Copenhagen Metro'', MA Transport economics, Institute for Transport Studies,  The University of Leeds.}

\bibitem{}{Martins-Filho, C. og Bin, O. (2005), ``Estimation of Hedonic Price function via Additive Nonparametric Regression'', \textit{Empirical Economics}, 30:93-114.}

\bibitem{}{Panduro, T. E., Lundhede, T. H. , Kummel, L., Ståhle, A., Heyman, A. og  Thorsen, B. J.(2013), ``Værdisætning af bykvaliteter – fra hovedstad til provins'' Institut for Fødevare- og ressourceøkonomi, Københavns Universitet.}

\bibitem{}{Wood, S.N. (2000), ``Modelling and smoothing parameter estimation with multiple quadratic penalties'',  \textit{J.R, Statist. Soc. B}, 62, part 2, pp. 413-428.}

\bibitem{}{Wood, S. N. (2003), ``Thin plate regression splines'', \textit{J.R. Statist. Soc. B} 65, pp. 95-114.}

\bibitem{}{Wooldridge, J. M.(2009), ``Introductory Econometrics'', \textit{South-western Cengage lerning}.}

\bibitem{}{Veie, K. L. (2013), ``Improved Methods for the Valuation of the enviroment in an Urban setting'', Københavns Universitet, PhD thesis.}

\bibitem{}{Bajic, V . (1983), ``The effects of a new subway line  on housing prices in metropolitan Toronto'', \textit{Urban studies}, vol. 20, pp. 147-158.}

\bibitem{}{Panduro, T. E., Veie, K., L. (2013), ``Classification and valuation of urban green spaces – a hedonic house price valuation'', \textit{Landscape and Urban planning} 120, pp. 119-128.}

\bibitem{}{Kiel, K. A., og Zabel, J. E. (2008), ``Location, Location, Location: The 3L approach to house price determination'',  \textit{Journal of housing economics}, vol. 17, issue 2, pp. 175-190.}

\bibitem{}{Geniaux, g. og Napoléone, C. (2008), ``Chapter 5: Semi-parametric Tools for spatial Hedonic models: an Introduction to Mixed Geographically Weighted Regression and Geoadditive models'', \textit{Hedonic Methods in Housing Markets}}

\bibitem{}{Zuur, A. F., Leno, E. N., Walker, N. J., Saveliev, A. A. og Smith, G. M.(2009), ``Things are not Always linear: Additive modelling, Chapter 3'', Mixed effects models and extensions in ecology with R, pp. 35-69.}

\bibitem{}{Zuur, A. F. (2012), ``A Beginner’s Guide to Generalized Additive Models with R'', \textit{Highland Statistics Ltd.}.}

\bibitem{}{Hastie, T. J. og Tibshirani, R. J.(1990), ``Generalized Additive Models'', \textit{Chapman \& Hall}.}

\bibitem{}{Pandoru, T. E. og Veie, K. L. (2013), ``An alternative to the standard spatial econometric approaches in hedonic house price models'', IFRO Working Paper 2013 /18.}

\bibitem{}{Agostini, C. A. og Palmucci, G. A.(2008), ``The anticipated Capitalisation Effect of a new Metro Line on housing Prices'', \textit{Fiscal Studies}, Vol. 29, no. 2, pp. 233-256.}

\bibitem{}{Sheppard, S. (1999), ``Chapter 41: Hedonic analysis of housing markets'', Handbook og Regional and urban economics,\textit{ Elsevier}.}

\bibitem{}{Palmquist, R. B. (2005), ``Chapter 16: Property value models'', Handbook og environmental economics, volume 2.,\textit{Elsevier}.}

\bibitem{}{Chernih, A. og Sherris, M. (2004), ``Geoadditive Hedonic Pricing Model''.}

\bibitem{}{Breheny, P. og Burchett, W. (2013), ``Visualization of Regression Models using visreg'', University of Kentucky.}

\bibitem{}{Andersen, R. (2014), ``Slides: 9. Generalized Additive Models'', \url{http://individual.utoronto.ca/andersen/soc6708/9.GAM.pdf} adgang d. 28 april 2014.}

\bibitem{}{Helbich, m., Brunauer, W., Vaz, E. og Nijkamp, p. (2013), ``Spatial Heterogeneity in Hedonic Price models: The case og Austria'', \textit{Tinbergen Institute discussion Paper}, TI 2013 – 171/VII.}

\bibitem{}{Rosen, S. (1974), ``Hedonic Prices and Implicit Markets: Product Differentiation in Pure Competition'', \textit{Journal of Political Economy}, Vol. 82, No. 1, pp. 34- 55.}

\bibitem{}{Wood, S. N. (2006), ``Generalized Additive Models: an introduction with R'', \textit{Chapman \& Hall}.}

\bibitem{}{Gundimeda, H. ``Hedonic price method – A concept Note'', \url{http://coe.mse.ac.in/dp/hedonic%20price.pdf} adgang d. 28. april 2014}   

\bibitem{}{Shaliza, C., ``Additive Models'',  undervisnings noter,  \url{
http://www.stat.cmu.edu/~cshalizi/350/lectures/21/lecture-21.pdf} adgang 28. april 2014}


\end{thebibliography}